Algomusicology, ????, Profit

### 2016-04-17 paper.tex
Incorporate @namin's citation protip.
Light drafting.

The insight that the inherent complexity of data can be measured by the length of the computer program needed to express it
originates with Andrey Kolmogorov\cite{On Tables of Random Numbers}. The Kolmogorov complexity of a piece of data is defined
as the length of the shortest program that evaluates to it.

@@

Meredith's answer is that by representing an analysis of a piece of music as a computer program, we can use Kolmogov complexity
to objectively measure the quality of the explanation it provides. A short program must necessarily capture a lot of the structure
of a piece, because summarising a piece's structure is the only way to achieve compression. A longer program is a worse explanation,
because it has missed opportunities to exploit the structure of the piece.

@@

@@

We can use this construction with an ASCII alphabet to obtain all possible ASCII strings.
This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges\cite{The Library of Babel}. In his
vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages.

The difference is that our sequence has all possible strings of all finite lengths.

@@

If we enumerate the Kleene star of a particular alphabet, we get a sequence of all its possible strings.
If we concatenate them all together into one long string, it produces what is known as a disjunctive sequence or lexicon.
A lexicon contains every finite string as a substring.

The results of the Kleene star are interesting from a Kolmogorov complexity perspective, because they can be described
concisely yet contain multitudes. Paradoxically, it displays the property that the whole is simpler than (almost all of)
the parts. That is, the Kolmogorov complexity of one string in our Library of Babel is more complicated to describe
than the Library taken as a whole.

Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
there must exist a book which is the formula and perfect compendium of all the rest". In other words, that one book
epitomises the complexity of the entire library.

@@

If pi's decimal expansion does have every possible combination of digits, then it's what is known as a disjunctive
sequence or lexicon. But we don't know for sure. No one has been able to prove it either way.

@@

'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'\cite{Got to Give It Up}
\cite{USA Today}.

>>>>

The insight that the inherent complexity of data can be measured by the length of the computer program needed to express it
originates with Andrey Kolmogorov\cite{On Tables of Random Numbers}. The Kolmogorov complexity of a piece of data is defined
as the length of the shortest program that evaluates to it. The greater the structural regularity, the more opportunities
to express the data using a short expression.

@@

Meredith's answer is that by representing an analysis of a piece of music as a computer program, we can use Kolmogov complexity
to objectively measure the quality of the explanation it provides. A short program must necessarily capture a lot of the structure
of a piece, because summarising a piece's structure is the only way to achieve compression. A longer program is a worse explanation,
because it has missed opportunities to exploit structural regularities in the piece.

@@

One might imagine that a maintainer of this musical code would refactor the former expression into the latter. Viewed this way,
refactoring away repetition can be seen as improving the explanatory power of the code.

@@

We can use this construction with an ASCII alphabet to obtain all possible ASCII strings. We might just as easily have
used the letters 'G', 'A', 'T' and 'C' to generate every possible DNA sequence.

This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges\cite{The Library of Babel}. In his
vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages. Melancholic
librarians spend their entire lives toiling in its maddiningly symetrical depths.

Some books exhibit apparent sense, most exhibit none. The narrator describes one that is "a mere labyrinth of letters,
but the next-to-last page says \textit|Oh time thy pyramids|."

Unlike Borges's library, our strings are not limited to four hundred and ten pages. Because of this limit, the Library of Babel
must either be finite, or have identical copies of the same book. Our list is an infinite sequence of all possible strings of
all finite lengths.

@@

If we enumerate the Kleene star of a particular alphabet, we get a sequence of all its possible strings.
If we concatenate them all together into one long string, it produces what is known as a disjunctive sequence or lexicon.
A lexicon contains every finite string as a substring. It's called a lexicon because it says everything that is possible
to say with that alphabet.

The results of the Kleene star are interesting from a Kolmogorov complexity perspective, because they can be described
concisely yet contain multitudes. Paradoxically, the whole is simpler than (almost all of) the parts.
That is, the Kolmogorov complexity of one string in our Library of Babel is more complicated to describe than the Library
taken as a whole.

Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
there must exist a book which is the formula and perfect compendium of all the rest". In other words, that one book
epitomises the complexity of the entire library, though it is part of the library.

@@

If pi's decimal expansion does have every possible combination of digits, then it's a lexicon for the decimal digits.
But we don't know for sure. No one has been able to prove it either way.

@@

'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
they were found to have infringed on the copyright of the Marvin Gaye song
'Got to Give It Up'\cite{Got to Give It Up, USA Today}.
